A first implementation of Section 3 of ``Bla Parabolic''

### 2019-08-02 Python/time/readme.tex
ODE solve fixed!

I've spent the past two weeks on a (not yet) linear time implementation of \S 3
from ``Bla Parabolic''. Currently it can only apply multiscale (mass) operator
in the time direction; I felt it was better to have a good understanding of one
aspect than to produce a half-baked implementation for the tensor-product case.

@@

\subsection{Some fun: solving an ODE}
I used the three-point basis on a uniform grid to solve some ODEs, in order
to test the (hopefully fast) application of the multiscale matrices inside an
iterative linear solver. I didn't completely succed, however.

My original goal was to solve $-u'' = f, u(0) = u(1) = 0$ using Galerkin on
both the singlescale and multiscale basis. See \texttt{ode\_test.py}. In
singlescale, it works perfectly and produces nice results (run the code). In
multiscale however, I was unable to find the right subset of indices to impose
a boundary condition on, in order to get results that were nice. I think I may
have solved a different equation entirely, maybe Rob will have some more ideas
(very likely, this idea was senseless). Still, I was able to solve the
``zeroth-order'' ODE $u = f$ by using the multiscale mass matrix. This is nice
enough.

>>>>

I've spent the past two weeks on a (practically but not theoretically) linear time implementation of \S 3
from ``Bla Parabolic''. Currently it can only apply multiscale (mass) operator
in the time direction; I felt it was better to have a good understanding of one
aspect than to produce a half-baked implementation for the tensor-product spacetime case.

@@

\subsection{Some fun: solving an ODE}
I used the three-point basis on a uniform grid to solve some ODEs, in order
to test the (hopefully fast) application of the multiscale matrices inside an
iterative linear solver. I solve $-u'' = f, u(0) = u(1) = 0$ using Galerkin on
both the singlescale and multiscale basis. See \texttt{ode\_test.py}. It works
perfectly and produces nice results (run \texttt{python3 ode\_test.py}). With a
small adaptation, this can be used to solve $u' = f$ and the like as well. Nice
little proof-of-concept :-)
